Robert C. Dunnell’s _Systematics in Prehistory_ at 50

### 2021-09-03 analysis/paper/paper.Rmd
update readme
update paper

@@

To survey the contribution that *Systematics in Prehistory* has made to evolutionary anthropology, we take inspiration from its concept of statistical clustering as a method for organising variability, and recent developments in the statistical analysis of text. We searched for items citing _Systematics in Prehistory_ on Google Scholar, downloaded all the search result pages (data were collected on July 2021), and extracted bibliographic data from each work citing *Systematics*. The raw data and R code for our analysis of the Google Scholar results are openly available online at http://doi.org/xxx/xxx.

@@

While the influence of *Systematics* has extended well beyond Dunnell's own primary study area of the US Southeast, there are some notable limits to its contributions. The Portuguese translation has received only 71 citations. In our data we also see only a single work in an East or Southeast Asian language, a book chapter in Japanese surveying the literature on cultural phylogenetics, indicating limited attention to _Systematics_ from researchers in the Eastern hemisphere. Could cultural differences in reasoning styles [@henrich2010weirdest] result in a diminished relevance for the philosophical content of _Systematics_ outside of Western academic communities? Or perhaps it is simply that the book is quite difficult to read, as noted by reviewers when it was first published ('confusion followed by grudging agreement' is how Spaulding [-@spaulding1974 p. 515-516] described his reaction to the book), and acknowledged by Dunnell in his forword to the 2002 edition. The low readability of the book likely limited the accessibility of its contents for readers whose first language is not English.

>>>>

Keywords: Systematics; Evolutionary archaeology; Cultural phylogenetics; Robert C. Dunnell

@@

To survey the contribution that *Systematics in Prehistory* has made to evolutionary anthropology, we take inspiration from its concept of statistical clustering as a method for organising variability, and recent developments in the statistical analysis of text. We searched for items citing _Systematics in Prehistory_ on Google Scholar, downloaded all the search result pages (data were collected on July 2021), and extracted bibliographic data from each work citing *Systematics*. The raw data and R code for our analysis of the Google Scholar results are openly available online at http://doi.org/10.17605/OSF.IO/JBPFW.

@@

While the influence of *Systematics* has extended well beyond Dunnell's own primary study area of the US Southeast, there are some notable limits to its contributions. The Portuguese translation has received only 71 citations, and the Spanish translation just 30. In our data we also see only a single work in an East or Southeast Asian language, a book chapter in Japanese surveying the literature on cultural phylogenetics, indicating limited attention to _Systematics_ from researchers in the Eastern hemisphere. Could cultural differences in reasoning styles [@henrich2010weirdest] result in a diminished relevance for the philosophical content of _Systematics_ outside of Western academic communities? Or perhaps it is simply that the book is quite difficult to read, as noted by reviewers when it was first published ('confusion followed by grudging agreement' is how Spaulding [-@spaulding1974 p. 515-516] described his reaction to the book), and acknowledged by Dunnell in his forword to the 2002 edition. The low readability of the book likely limited the accessibility of its contents for readers whose first language is not English.
